The \dealii{} Library, Version 8.5

### 2017-03-20 8.5/paper.tex
Make Reynolds not possessive.
edit the edits

\texttt{CellDataStorage} can work with arbitrary kinds of data defined
to live on a cell as long as the corresponding data type implements a
certain interface. As an example,
the abstract class \texttt{TransferableQuadraturePointData} provides
a generic interface to facilitate several low-level operations
that were previously tedious or technically challenging to implement.
For instance, when a user's custom data type is derived from \texttt{TransferableQuadraturePointData}
-- a data type that stores information at the quadrature points of cells using
\texttt{CellDataStorage} --,
then the \texttt{parallel::distributed::ContinuousQuadratureDataTransfer} class
can transfer this data during
$h$-adaptive refinement from parent to children and the other way around
(interpreting the data on quadrature points as discrete representations of an
underlying continuous field),
as well as from one processor to another during repartitioning.

@@

 \item {\bf step-57} solves the stationary Navier-Stokes equations.
 The nonlinear system is solved using Newton's method on a sequence of adaptively refined
 grids. The preconditioner is again built on a block factorization of the saddle point
 system like in step-55 and step-56, but the non-symmetric terms stemming from the
 nonlinear convective part requires more sophisticated solvers. The benchmark problem,
 flow in the 2d lid-driven cavity, requires a continuation method for high Reynold's 
 numbers.
 \end{itemize}

>>>>

\texttt{CellDataStorage} can work with arbitrary kinds of data defined to live on a cell
as long as the corresponding data type implements a default constructor.
Additionally, when a user's custom data type is derived from \texttt{TransferableQuadraturePointData}
and thereby implements certain interface,
then the \texttt{parallel::distributed::ContinuousQuadratureDataTransfer} class
can transfer this data during $h$-adaptive refinement from parent cell to children
(interpreting the data on quadrature points as discrete representations of an
underlying continuous field),
as well as from one processor to another during repartitioning.

@@

 \item {\bf step-57} solves the stationary Navier-Stokes equations.
 The nonlinear system is solved using Newton's method on a sequence of adaptively refined
 grids. The preconditioner is again built on a block factorization of the saddle point
 system like in step-55 and step-56, but the non-symmetric terms stemming from the
 nonlinear convective part requires more sophisticated solvers. The benchmark problem,
 flow in the 2d lid-driven cavity, requires a continuation method for high Reynolds
 numbers.
 \end{itemize}
